Measuring causal influence with\\ back-to-back regression

### 2019-05-22 paper/meg_exps.tex
small fix meg_exps

We show all the feature coefficients as a function of time in the stacked plots,
Figure \ref{fig:megresult}. Our method confirms previous findings in
neuroscience literature. In particular, \cite{kutas2011thirty} find that word
frequency correlates with a brain wave around 400ms. Similarly,
\cite{pegado2014timing} show that letter strings correlate with early brain
responses. Both these phenomena can be observed in Figures
\label{fig:meg_twocurves} and \ref{fig:megresult}, where we show that our
method is able to separate them more clearly than the forward regression
approach.

>>>>

We show all the feature coefficients as a function of time in the stacked plots,
Figure \ref{fig:megresult}. Our method confirms previous findings in
neuroscience literature. In particular, \cite{kutas2011thirty} find that word
frequency correlates with a brain wave around 400ms. Similarly,
\cite{pegado2014timing} show that letter strings correlate with early brain
responses. Both these phenomena can be observed in Figures
\ref{fig:meg_twocurves} and \ref{fig:megresult}, where we show that our
method is able to separate them more clearly than the forward regression
approach.
